### 2015-03-24 cv-body.tex
CV tweaks

\begin{description}
\itemsep1pt\parskip0pt\parsep0pt
\item[2011--15]
Ph.D.\ Biology, Simon Fraser University, Burnaby, Canada\\ Supervisors:
Dr.\ Nicholas K. Dulvy and Dr.\ Andrew B. Cooper\\ Canadian Fulbright
Scholar to the University of Washington in 2012--13
\item[2008--10]
M.Sc.\ Biology, Dalhousie University, Halifax, Canada\\ Thesis title:
Trends, drivers, and ecosystem effects of expanding global invertebrate
fisheries. Supervisor: Dr.\ Heike K. Lotze.
(\href{http://seananderson.ca/papers/Anderson_MSc_2010.pdf}{PDF})\\
Canadian \href{http://goo.gl/nA1zE}{Governor General's Academic Gold
Medal} for the top-ranked Master's Natural Sciences and Engineering
thesis at Dalhousie University in 2010
\item[2004--07]
B.Sc.\ (Hons.) Environmental Science, Dalhousie University, Halifax,
Canada\\ Thesis title: How sustainable are emerging low-trophic level
fisheries on the Scotian Shelf? Supervisors: Dr.\ Heike K. Lotze and
Dr.\ Ransom A. Myers.
(\href{http://seananderson.ca/papers/Anderson_HSc_2006.pdf}{PDF})\\
First Class Honours \& Environmental Programmes Honour Society Medal
\item[2001--03]
B.Sc.\ Candidate (Hons.) Kinesiology, University of Waterloo, Waterloo,
Canada Transferred to Dalhousie University in 2004.
\end{description}

@@

@@

Marine Science. In press. \url{http://doi.org/10.1093/icesjms/fsu198}.

@@

@@

Marine Science. In press. \url{http://doi.org/10.1093/icesjms/fsu055}
In press. \url{http://doi.org/10.1093/icesjms/fsu007}

@@

\begin{description}
\itemsep1pt\parskip0pt\parsep0pt
\item[2015]
Orzechowski, E.A., R. Lockwood, J.E. Byrnes, \textbf{S.C. Anderson}, S.
Finnegan, Z.V. Finkel, P.G. Harnik, D.R. Lindberg, L.H. Liow, H.K.
Lotze, C.R. McClain, J.L. McGuire, A. O'Dea, J.M. Pandolfi, C. Simpson,
D.P. Tittensor. Determinants of extinction selectivity over the last 500
million years: a meta-analysis of marine bivalves and gastropods. In
revision.
\item[2015]
Finnegan*, S., \textbf{S.C. Anderson}*, P.G. Harnik*, C. Simpson, D.P.
Tittensor, J.E. Byrnes, Z.V. Finkel, D.R. Lindberg, L.H. Liow, R.
Lockwood, H.K. Lotze, C.M. McClain, J.L. McGuire, A. O'Dea, J.M.
Pandolfi. Paleontological baselines for evaluating extinction risk in
the modern oceans. In review. (*Authors contributed equally).
\item[2015]
Trebilco, R., N.K. Dulvy, \textbf{S.C. Anderson}, A.K. Salomon. The
paradox of inverted biomass pyramids in kelp forest fish communities. In
revision.
\end{description}

@@

\begin{description}
\itemsep1pt\parskip0pt\parsep0pt
\item[2015]
David H. Smith Conservation Postdoctoal Research Fellowship
\item[2015]
Natural Sciences and Engineering Research Council of Canada Postdoctoral
Fellowship
\item[2014]
Garfield Weston Foundation / BC Packers Ltd. Graduate Fellowship in
Marine Sciences
\item[2014]
Graduate Fellowship (two semesters), Simon Fraser University
\item[2012--13]
Canadian Fulbright Scholar award to the University of Washington in
2012--13
\item[2011]
Canadian \href{http://goo.gl/nA1zE}{Governor General's Academic Gold
Medal} for the top-ranked Master's Natural Sciences and Engineering
thesis at Dalhousie University in 2010
\item[2011--14]
Provost Prize of Distinction, Simon Fraser University
\item[2011--14]
Natural Sciences and Engineering Research Council of Canada Postgraduate
Scholarship (Doctoral)
\item[2007--10]
Faculty Research Grant Scholarship, Dalhousie University
\item[2007--09]
Graduate Studies Scholarship, Dalhousie University
\item[2007]
Environmental Programmes Honour Society Medal, Dalhousie University
\end{description}

@@

\begin{description}
\itemsep1pt\parskip0pt\parsep0pt
\item[2013--14]
Organizer of Stats Beerz --- a statistical help group attended by
graduate students and postdocs primarily in the Earth to Oceans research
group, but also the wider SFU Biology and Geography Departments, and the
School of Resource and Environmental Management (REM).
\item[2014]
Developed self-directed lecture and exercises on ggplot2 for FISH 554:
Beautiful graphics in R, School of Aquatic and Fishery Sciences,
University of Washington, Seattle, WA, United States.\\
\url{https://github.com/seananderson/ggplot2-FISH554}
\item[2013]
Two-part workshop on data manipulation for Stats Beerz and Earth to
Oceans groups at Simon Fraser University with approximately 25
participants. An introduction to plyr, advanced concepts with plyr and
function debugging, and an introduction to dplyr.\\
\url{https://github.com/seananderson/plyr-statsbeerz}
\item[2013]
Instructor for BISC-888-1: Data Wrangling and Visualization in R, a
graduate-level course at Simon Fraser University, Burnaby, BC, Canada
with approximately 20 participants. Co-developed curriculum and
developed/delivered lectures, exercises, notes, and assignments for
three of six two-hour classes.\\
\url{https://github.com/seananderson/datawranglR} (see classes 03, 04,
05)
\item[2012]
Introduction to ggplot2.
(\href{http://seananderson.ca/courses/12-ggplot2/ggplot2_notes.pdf}{notes},
\href{http://seananderson.ca/courses/12-ggplot2/ggplot2_slides_with_examples.pdf}{slides})
Lecture for FISH 507H: Beautiful Graphics in R, School of Aquatic and
Fishery Sciences, University of Washington, Seattle, WA, United States
\item[2012]
Workshop on the R package plyr.
(\href{http://seananderson.ca/courses/12-plyr/plyr_2012.pdf}{notes},
\href{http://seananderson.ca/courses/12-plyr/plyr_2012_slides.pdf}{slides},
\href{http://seananderson.ca/courses/12-plyr/plyr_2012_examples.html}{examples})
Branch Lab, School of Aquatic and Fishery Sciences, University of
Washington, Seattle, WA, United States
\item[2011]
Multipanel plotting in R with base graphics.
(\href{http://seananderson.ca/courses/11-multipanel/multipanel.pdf}{notes},
\href{http://seananderson.ca/courses/11-multipanel/multipanel-slides.pdf}{slides}).
Earth2Ocean Research Group, Simon Fraser University, Burnaby, BC,
Canada.
\item[2011]
A brief introduction to R.
(\href{http://seananderson.ca/courses/11-rintro/RIntro.pdf}{notes},
\href{http://seananderson.ca/courses/11-rintro/RIntro.R}{workshop
code}). Earth2Ocean Research Group, Simon Fraser University, Burnaby,
BC, Canada.
\item[2011]
Workshop on the R package plyr
(\href{http://seananderson.ca/courses/11-plyr/plyr.pdf}{notes},
\href{http://seananderson.ca/courses/11-plyr/plyr-slides.pdf}{slides}).
Earth2Ocean Research Group, Simon Fraser University, Burnaby, BC,
Canada.
\item[2007--08]
Teaching Assistant, Organismal Biology and Ecology, Dalhousie
University, two semesters (BIOL 1021).
\item[2007--08]
Teaching Assistant, Marine Mammology, Dalhousie University (BIOL 4060).
\end{description}

@@

\begin{description}
\itemsep1pt\parskip0pt\parsep0pt
\item[2013]
Co-developed a set of maps showing trends in global fisheries status for
the front page of \href{http://ramlegacy.org/}{ramlegacy.org}, the RAM
Legacy Stock Assessment Database (for Dr.\ Ray Hilborn).
\item[2011--12]
Database management for the project \emph{Global Shark Abundance
Baselines} (Hopkins Marine Station, Stanford University, CA, United
States) with F. Micheli, F. Ferretti, N.K. Dulvy, H.K. Lotze, and B.
Worm.
\item[2010]
Assessment of Arctic surfclam on Banquereau Bank using
industry-collected data for Clearwater Seafoods, Bedford, NS, Canada.
\item[2010]
Modelling length-frequency distribution changes of Atlantic halibut for
NAFO Divisions 4VWX5Z and 3NOP for Dr.\ K. Trzcinski, Population Ecology
Division, Bedford Institute of Oceanography, Fisheries and Oceans,
Dartmouth, NS, Canada.
\end{description}

>>>>

\begin{description}
\itemsep1pt\parskip0pt\parsep0pt
\item[2011--15]
Ph.D.\ Biology, Simon Fraser University, Burnaby, Canada\\ Variance and
extreme events in population ecology\\ Supervisors: Dr.\ Nicholas K.
Dulvy and Dr.\ Andrew B. Cooper\\ Canadian Fulbright Scholar to the
University of Washington in 2012--13
\item[2008--10]
M.Sc.\ Biology, Dalhousie University, Halifax, Canada\\ Trends, drivers,
and ecosystem effects of expanding global invertebrate fisheries\\
Supervisor: Dr.\ Heike K. Lotze.
(\href{http://seananderson.ca/papers/Anderson_MSc_2010.pdf}{PDF})\\
Canadian \href{http://goo.gl/nA1zE}{Governor General's Academic Gold
Medal} for the top-ranked Master's Natural Sciences and Engineering
thesis at Dalhousie University in 2010
\item[2004--07]
B.Sc.\ (Hons.) Environmental Science, Dalhousie University, Halifax,
Canada\\ Thesis title: How sustainable are emerging low-trophic level
fisheries on the Scotian Shelf? Supervisors: Dr.\ Heike K. Lotze and
Dr.\ Ransom A. Myers.
(\href{http://seananderson.ca/papers/Anderson_HSc_2006.pdf}{PDF})\\
First Class Honours \& Environmental Programmes Honour Society Medal
\item[2001--03]
B.Sc.\ Candidate (Hons.) Kinesiology, University of Waterloo, Waterloo,
Canada Transferred to Dalhousie University in 2004.
\end{description}

@@

Finnegan*, S., \textbf{S.C. Anderson}*, P.G. Harnik*, C. Simpson, D.P.
Tittensor, J.E. Byrnes, Z.V. Finkel, D.R. Lindberg, L.H. Liow, R.
Lockwood, H.K. Lotze, C.M. McClain, J.L. McGuire, A. O'Dea, J.M.
Pandolfi. Paleontological baselines for evaluating extinction risk in
the modern oceans. In press. (\emph{*Authors contributed equally}).

@@

Marine Science. 72(1): 99--110.
\url{http://doi.org/10.1093/icesjms/fsu198}.

@@

Marine Science. 72(1): 137--150.
\url{http://doi.org/10.1093/icesjms/fsu055}
72(1): 31--43. \url{http://doi.org/10.1093/icesjms/fsu007}

@@

@@

\begin{description}
\itemsep1pt\parskip0pt\parsep0pt
\item[2015]
Orzechowski, E.A., R. Lockwood, J.E. Byrnes, \textbf{S.C. Anderson}, S.
Finnegan, Z.V. Finkel, P.G. Harnik, D.R. Lindberg, L.H. Liow, H.K.
Lotze, C.R. McClain, J.L. McGuire, A. O'Dea, J.M. Pandolfi, C. Simpson,
D.P. Tittensor. Determinants of extinction selectivity over the last 500
million years: a meta-analysis of marine bivalves and gastropods. In
revision.
\item[2015]
Trebilco, R., N.K. Dulvy, \textbf{S.C. Anderson}, A.K. Salomon. The
paradox of inverted biomass pyramids in kelp forest fish communities. In
revision.
\end{description}

@@

\begin{description}
\itemsep1pt\parskip0pt\parsep0pt
\item[2015]
David H. Smith Conservation Postdoctoral Research Fellowship
\item[2015]
Natural Sciences and Engineering Research Council of Canada Postdoctoral
Fellowship
\item[2014]
Garfield Weston Foundation / BC Packers Ltd. Graduate Fellowship in
Marine Sciences
\item[2014]
Graduate Fellowship (two semesters), Simon Fraser University
\item[2012--13]
Canadian Fulbright Scholar award to the University of Washington in
2012--13
\item[2011]
Canadian \href{http://goo.gl/nA1zE}{Governor General's Academic Gold
Medal} for the top-ranked Master's Natural Sciences and Engineering
thesis at Dalhousie University in 2010
\item[2011--14]
Provost Prize of Distinction, Simon Fraser University
\item[2011--14]
Natural Sciences and Engineering Research Council of Canada Postgraduate
Scholarship (Doctoral)
\item[2007--10]
Faculty Research Grant Scholarship, Dalhousie University
\item[2007--09]
Graduate Studies Scholarship, Dalhousie University
\item[2007]
Environmental Programmes Honour Society Medal, Dalhousie University
\end{description}

@@

\begin{description}
\itemsep1pt\parskip0pt\parsep0pt
\item[2014--15]
Developed self-directed lecture and exercises on ggplot2 for FISH 554:
Beautiful graphics in R, School of Aquatic and Fishery Sciences,
University of Washington, Seattle, WA, United States.\\
\url{http://seananderson.ca/ggplot2-FISH554/}
\item[2013--14]
Organizer of Stats Beerz --- a statistical help group attended by
graduate students and postdocs primarily in the Earth to Oceans research
group, but also the wider SFU Biology and Geography Departments, and the
School of Resource and Environmental Management (REM).
\item[2013]
Two-part workshop on data manipulation for Stats Beerz and Earth to
Oceans groups at Simon Fraser University with approximately 25
participants. An introduction to plyr, advanced concepts with plyr and
function debugging, and an introduction to dplyr.\\
\url{https://github.com/seananderson/plyr-statsbeerz}
\item[2013]
Instructor for BISC-888-1: Data Wrangling and Visualization in R, a
graduate-level course at Simon Fraser University, Burnaby, BC, Canada
with approximately 20 participants. Co-developed curriculum and
developed/delivered lectures, exercises, notes, and assignments for
three of six two-hour classes.\\
\url{https://github.com/seananderson/datawranglR} (see classes 03, 04,
05)
\item[2012]
Introduction to ggplot2.
(\href{http://seananderson.ca/courses/12-ggplot2/ggplot2_notes.pdf}{notes},
\href{http://seananderson.ca/courses/12-ggplot2/ggplot2_slides_with_examples.pdf}{slides})
Lecture for FISH 507H: Beautiful Graphics in R, School of Aquatic and
Fishery Sciences, University of Washington, Seattle, WA, United States
\item[2012]
Workshop on the R package plyr.
(\href{http://seananderson.ca/courses/12-plyr/plyr_2012.pdf}{notes},
\href{http://seananderson.ca/courses/12-plyr/plyr_2012_slides.pdf}{slides},
\href{http://seananderson.ca/courses/12-plyr/plyr_2012_examples.html}{examples})
Branch Lab, School of Aquatic and Fishery Sciences, University of
Washington, Seattle, WA, United States
\item[2011]
Multipanel plotting in R with base graphics.
(\href{http://seananderson.ca/courses/11-multipanel/multipanel.pdf}{notes},
\href{http://seananderson.ca/courses/11-multipanel/multipanel-slides.pdf}{slides}).
Earth2Ocean Research Group, Simon Fraser University, Burnaby, BC,
Canada.
\item[2011]
A brief introduction to R.
(\href{http://seananderson.ca/courses/11-rintro/RIntro.pdf}{notes},
\href{http://seananderson.ca/courses/11-rintro/RIntro.R}{workshop
code}). Earth2Ocean Research Group, Simon Fraser University, Burnaby,
BC, Canada.
\item[2011]
Workshop on the R package plyr
(\href{http://seananderson.ca/courses/11-plyr/plyr.pdf}{notes},
\href{http://seananderson.ca/courses/11-plyr/plyr-slides.pdf}{slides}).
Earth2Ocean Research Group, Simon Fraser University, Burnaby, BC,
Canada.
\item[2007--08]
Teaching Assistant, Organismal Biology and Ecology, Dalhousie
University, two semesters (BIOL 1021).
\item[2007--08]
Teaching Assistant, Marine Mammology, Dalhousie University (BIOL 4060).
\end{description}

@@

\begin{description}
\itemsep1pt\parskip0pt\parsep0pt
\item[2013]
Co-developed global fisheries status maps for the
\href{http://ramlegacy.org/}{RAM Legacy Stock Assessment Database} for
R. Hilborn
\item[2010]
Assessment of Arctic surfclam on Banquereau Bank using
industry-collected data for Clearwater Seafoods, Bedford, NS, Canada.
\item[2010]
Modelling length-frequency distribution changes of Atlantic halibut for
NAFO Divisions 4VWX5Z and 3NOP for Dr.\ K. Trzcinski, Population Ecology
Division, Bedford Institute of Oceanography, Fisheries and Oceans,
Dartmouth, NS, Canada.
\end{description}
